The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-03 SI.tex
address many motors (#33)

>>>>

Each message call over the yaq interface returns rapidly,
ensuring that client applications are not blocked. Some mes-
sages initiate long-running operations, e.g. motor motion and
sensor measurement. Separate messages are provided to re-
trieve results from e.g. sensor measurement. In order to know
how long to wait, all yaq daemons provide a message called
“is\_busy”, which returns "true" while the long running action
is not complete, and "false" once it is finished. Additionally,
multiple clients can communicate with the same daemon si-
multaneously. A complex instrument may involve multiple
operators watching sensor data in real time, while one pro-
gram is orchestrating the hardware and recording the data.
